### 2022-01-18 src-latex/parts/20-related-work.tex
Reduced sections 2 and 3

The directory processing pipeline presented in \cite{bell2020automated} to locate old gas stations using mid-20th century directories includes an OCR step, done with Tesseract, and a NER step to identify company names and addresses within the extracted text, performed using rules built as regular expressions.
This section reviews existing approaches to achieving each of these two tasks. It concludes with a review of the works assessing the effects of OCR quality on the NER performance and the proposed solutions to overcome this problem.

@@

\nathalie{à compléter/retoucher}

@@

Many approaches have been designed to recognize named entities, ranging from handcrafted rules to supervised approaches \cite{nadeau2007}.
Rule based approaches look for portions of text that match patterns based on word characteristics such as their case, whether they are digits or not, their part-of-speech tags, etc.
These patterns can be fully handcrafted like in \cite{bell2020automated} or generated by data mining approaches like in \cite{nouvel2011}.
Rule based approaches can also combine a set of patterns with a set of dictionaries (gazetteers, author lists, etc.) that help recognizing named entities when an exhaustive lexicon of searched entities is available \cite{mansouri2008,maurel2011}.
For example, the CasEN\footnote{\url{https://tln.lifat.univ-tours.fr/version-francaise/ressources/casen}} transducer cascade leverages syntactic lexical patterns and dictionaries to recognize Named Entities in French texts.
Such kind of approaches achieve very good results when applied to specialized domain corpus - like directories - and when an exhaustive lexicon are available, but at high system engineering cost \cite{nadeau2007}.

Supervised approaches include both approaches implementing supervised learning algorithms with careful text feature engineering, and deep learning based approaches which automatically build their own features to classify words into one category of named entities or another.
In recent years, the latter have grown dramatically, yielding state-of-the-art performances and establishing new baselines\cite{li2020}.
A recent survey proposed by \cite{li2020} presents deep learning techniques for NER according to the distributed representation(s) they use as input, their context encoder and their tag decoder.
It shows that language model embeddings pretrained using \textit{Transformer} \cite{vaswani2017attention}, like BERT \cite{devlin2018bert}, can not only be used to replace traditional embeddings as input distributed representations but also be fine-tuned for the NER task with one additional output layer while achieving state-of-the-art performances.
The survey concludes that fine-tuning general-purpose contextualized language models with domain-specific data is very likely to give good performance for use cases with domain-specific texts and few training data.

@@

\cite{Labusch2020NamedED} applied a BERT-based NER model to historical texts in German, French, and English, produced by OCR.
It is off-the-shelf multilingual BERT-based NER model, pretrained on more than 2 000 000 pages of OCRed historical texts in three languages and fine-tuned on historical texts NER ground truth, also in three languages.
Eventually, a clear decrease in NER performance on OCRed texts is noted. Moreover, the article reports that this decrease is more important for English texts for which the OCR is of poorer quality than for texts in the other two languages.

Several recent studies have focused on the extent to which the quality of the OCR affects the results produced by a NER model.
\cite{van2020assessing} assess the impact of OCR on several NLP downstream tasks, including NER. They worked on a corpus published by a post-OCR correction software company, made of many journal articles with different levels of OCR errors and their respective ground truths.
For each OCRed article, the Word Error Rate (WER) is computed and the English model \textit{en-core-web-lg} provided by Spacy\footnote{\url{https://spacy.io/}} library is used to perform NER on \textit{Person}, \textit{GPE} and \textit{Date}.
The performance of the NER model with respect to OCR quality is eventually assessed by calculating the F-measure for each NER class, and each article i.e., each WER value.
\cite{hamdi2020assessing} performed a similar but more extensive evaluation on four different NER models: CoreNLP using Conditional Random Fields and three deep neural models, BLSTM-CNN, BLSTM-CRF, and BLSTM-CNN-CRF.
They tested them on two well-known NER benchmark corpora: CoNLL-02 and CoNLL-03. They applied four different types of OCR noise to each corpus, with two levels of degradation and computed the WER and Character Error Rate (CER) for each degraded version.
Finally, they applied each NER model to the progressively degraded versions of the corpus and computed the resulting F-measure.
Overall, NER F-score drops from 90\% to 50\% when the WER increase from 8\% to 50\%. Besides, all NER models are sensitive to OCR errors, but models based on deep neural networks seem less prone to errors.

Based on the observation that OCR errors necessarily affect the performance of NER models applied to historical texts, \cite{huynh2020use} and \cite{marz2021data} have proposed different approaches to reduce their negative impact.
The former uses a spelling correction tool on several corpora with variable OCR error rates, to assess whether spelling correction has a beneficial impact on NER performance or not.
The results showed that as long as OCR errors remain low (CER<2\% and WER<10\%), the F-measure of NER results remains stable.
It starts to decrease significantly when OCR errors exceed these thresholds.
The latter work focuses on adapting the training data to facilitate the generalization of an off-the-shelf NER model from modern texts to historical texts.
Three different NER models are tested on three historical corpora, in French, English, and Dutch. The best results are produced by a model trained on clean modern data, including many  embeddings as input (FastText, character and multilingual Flair embeddings, BERT and historical embeddings computed with Flair on a historical corpus), and fine-tuned on a noisy historical ground truth.

In conclusion, NER approaches based on deep learning seem to be more suitable for dealing with historical texts as they adapt more easily to OCR errors than rule-based approaches.
Recent work in this area suggests that the impact of OCR quality on NER can be reduced by using different strategies.
On the one hand, if the OCR error rate is kept below a certain threshold, the NER models remain little impacted: it is therefore important to reduce OCR errors as much as possible, but a low error rate may remain acceptable.
On the other hand, it seems beneficial to reuse a NER model trained on modern data and adapt it to historical texts using supervised or unsupervised approaches.

>>>>

The directory processing pipeline presented in \cite{bell2020automated} includes an OCR step, done with Tesseract, and a NER step to identify company names and addresses, performed using regular expressions.
This section reviews existing OCR and NER approaches with historical texts and presents some works assessing the effects of OCR quality on the NER performance and the proposed solutions.

@@

\nathalie{à compléter/retoucher?}

@@

Many approaches have been designed to recognize named entities, ranging from handcrafted rules to supervised approaches \cite{nadeau2007}.
Rule based approaches look for portions of text that match patterns based on word characteristics such as their case, their part-of-speech tags, etc.
These patterns can be fully handcrafted like in \cite{bell2020automated} or generated by data mining approaches like in \cite{nouvel2011}.
Rule based approaches can also combine a set of patterns with a set of dictionaries (gazetteers, author lists, etc.) that help recognizing named entities when an exhaustive lexicon of searched entities is available \cite{mansouri2008,maurel2011}.
%For example, the CasEN\footnote{\url{https://tln.lifat.univ-tours.fr/version-francaise/ressources/casen}} transducer cascade leverages syntactic lexical patterns and dictionaries to recognize Named Entities in French texts.
Such kind of approaches achieve very good results when applied to specialized domain corpus - like directories - and when an exhaustive lexicon are available, but at high system engineering cost \cite{nadeau2007}.

Supervised approaches include both approaches implementing supervised learning algorithms with careful text feature engineering, and deep learning based approaches which automatically build their own features to classify tokens into named entity categories.
In recent years, the latter have grown dramatically, yielding state-of-the-art performances and establishing new baselines\cite{li2020}.
A recent survey proposed by \cite{li2020} presents deep learning techniques for NER according to the distributed representation(s) they use as input, their context encoder and their tag decoder.
It shows that language model embeddings pretrained using \textit{Transformer} \cite{vaswani2017attention}, like BERT \cite{devlin2018bert}, can not only be used to replace traditional embeddings as input distributed representations but also be fine-tuned for the NER task with one additional output layer while achieving state-of-the-art performances.
The survey concludes that fine-tuning general-purpose contextualized language models with domain-specific data is very likely to give good performance for use cases with domain-specific texts and few training data.

@@

\cite{Labusch2020NamedED} pretrained an off-the-shelf multilingual BERT-based NER model on more than 2 000 000 pages of OCRed historical texts in German, French, and English. They fine-tuned it on historical texts NER ground truth, also in these three languages and tested it on OCRed historical texts in each language.
Eventually, a clear decrease in NER performance on OCRed texts is noted, especially for the English texts for which the OCR is of poorer quality.

Several recent studies have focused on the extent to which the quality of the OCR affects the results produced by a NER model.
\cite{van2020assessing} assess the impact of OCR on several NLP downstream tasks, including NER. They worked on a corpus published by a post-OCR correction software company, made of many journal articles with different levels of OCR errors and their respective ground truths.
For each OCRed article, the Word Error Rate (WER) is computed and the English model \textit{en-core-web-lg} provided by Spacy\footnote{\url{https://spacy.io/}} library is used to perform NER on \textit{Person}, \textit{GPE}\footnote{Geopolitical Entity} and \textit{Date}.
The performance of the NER model with respect to OCR quality is eventually assessed by computing the F-measure for each NER class, and each article i.e., each WER value.
\cite{hamdi2020assessing} performed a similar but more extensive evaluation on four different NER models: CoreNLP using Conditional Random Fields and three deep neural models, BLSTM-CNN, BLSTM-CRF, and BLSTM-CNN-CRF.
They tested them on two well-known NER benchmark corpora: CoNLL-02 and CoNLL-03. They applied four different types of OCR noise to each corpus, with two levels of degradation and computed the WER and Character Error Rate (CER) for each degraded version.
Finally, they applied each NER model to the progressively degraded versions of the corpus and computed the resulting F-measure.
Overall, NER F-measure drops from 90\% to 50\% when the WER increase from 8\% to 50\%. However, models based on deep neural networks seem less sensitive to OCR errors.

\cite{huynh2020use} and \cite{marz2021data} have proposed different approaches to reduce the negative impact of OCR errors on NER performance with historical texts.
The former uses a spelling correction tool on several corpora with variable OCR error rates, to assess whether NER performance benefit from spelling corrections or not.
As long as OCR errors remain low (CER<2\% and WER<10\%), the F-measure of NER results remains stable.
It starts to decrease significantly when OCR errors exceed these thresholds.
The latter work focuses on adapting the training data to facilitate the generalization of an off-the-shelf NER model from modern texts to historical texts.
Three different NER models are tested on three historical corpora, in French, English, and Dutch. The best results are produced by a model trained on clean modern data, including embeddings computed with Flair on a historical corpus, and fine-tuned on a noisy historical ground truth.

In conclusion, NER approaches based on deep learning seem to be more suitable for dealing with historical texts as they adapt more easily to OCR errors than rule-based approaches.
Recent work in this area suggests that the impact of OCR quality on NER can be reduced by using different strategies.
On the one hand, if the OCR error rate is kept below a certain threshold, the NER models remain little impacted: it is therefore important to reduce OCR errors as much as possible, but a low error rate may remain acceptable.
On the other hand, reusing a NER model trained on modern data and adapted to historical texts using supervised or unsupervised approaches seems a good strategy.

### 2022-01-18 src-latex/parts/30-dataset.tex
Reduced sections 2 and 3

In this work, we made a selection among the available directories, trying our best to retain copies representative of the diversity of existing directories and of sufficient quality to produce a reliable training data set. The Table \ref{tab:directories} lists the directories selected, their layout, the structure of their entries, and the number of annotated entries according to the indexes considered. For example, the Didot directory of 1854 is organised according to three indexes: by name, by activity, and by street name. The structure of the following entry is characteristic of its index by name: "Batton (D.-A.) *, professeur au Conservatoire de musique et de déclamation, Saint-Georges, 47." This entry begins with a person's name, followed by the initials of their first name in parentheses.The star symbol indicates that this person was awarded the Légion d'Honneur. The following part of this entry represents the person's activity,i.e. their profession, or social status, here "professor at the Conservatory of music and declamation". The street name and number where the person lives or carries out their activity are written at the end of the entry. These pieces of information constituting the structure of the entries are the basic data that we want to extract, deduplicate and structure in order to build a spatio-temporal database of XIX\textsuperscript{th} century Parisian inhabitants and businesses. With the exception of some potentially wordy activity descriptions, most of these pieces of information correspond to named entities. However, as Table \ref{tab:directories} shows, while most entries contain the same types of named entities, the order in which they appear and the way they are written vary from one directory to another. This argues for a supervised, rather than rule-based, NER approach, which requires annotated data.

@@

\subsection{Assessing the groundtruth quality}

Our dataset is thus made of excerpts

TODO interesting points to detail:
\begin{itemize}
    \item statistics about entry lengths (histogram of number of char / tokens par entry)
    \item entities we considered and how we annotated them (how we assessed gold's quality)
    \item statistics on the distribution of entities across directories and their arrangement within entries
    \item OCR data (automated systems and clean text + how we created the "clean" text + whether/how we assessed clean text's quality)
    \item Measure inter-annotator agreement ? 
    \item Explain charset projection
    \item \dots
\end{itemize}

>>>>

For training as testing purposes, our groundtruth dataset must be as representative as possible of the diversity of the available directories. The Table \ref{tab:directories} lists the directories selected, their layout, the structure of their entries, and the number of annotated entries according to the considered index.

For example, the Didot directory of 1854 is organised according to three indexes: by name, by activity, and by street name. The structure of the following entry is characteristic of its index by name: "Batton (D.-A.) \scalerel*{\includegraphics{./images/LH.png}}{H}, professeur au Conservatoire de musique et de déclamation, Saint-Georges, 47." This entry begins with a person's name, followed by the initials of their first name in parentheses.The symbol indicates that this person was awarded the Légion d'Honneur. The following part of this entry represents the person's activity,i.e. their profession, or social status, here "professor at the Conservatory of music and declamation". The street name and number where the person lives or carries out their activity are written at the end of the entry.

These pieces of information constituting the structure of the entries are the basic data that we want to extract, deduplicate and structure in order to build a spatio-temporal database of XIX\textsuperscript{th} century Parisian inhabitants and businesses. With the exception of some potentially wordy activity descriptions, they correspond to named entities. However, as Table \ref{tab:directories} shows, while most entries contain the same types of named entities, their order and the way they are written vary from one directory or index to another. To provide examples of each entry structure, pages from each type have thus been annotated\footnote{In this work, the street name index entries have not been included as they are very different from the others. The strategy to be adopted to process them without loss of quality for the NER model will be the subject of future work.}.

@@

\subsection{Assessing the groundtruth quality}
\nathalie{On va utiliser cette sous-section ou pas?}
Our dataset is thus made of excerpts TODO interesting points to detail:

\begin{itemize}
    \item statistics about entry lengths (histogram of number of char / tokens par entry)
    \item entities we considered and how we annotated them (how we assessed gold's quality)
    \item statistics on the distribution of entities across directories and their arrangement within entries
    \item OCR data (automated systems and clean text + how we created the "clean" text + whether/how we assessed clean text's quality)
    \item Measure inter-annotator agreement ? 
    \item Explain charset projection
    \item \dots
\end{itemize}

### 2022-01-18 src-latex/parts/40-ner-approaches.tex
Reduced sections 2 and 3

Previous work on the influence of OCR errors on NER models shows that it is preferable to reuse a model trained on modern data and adapt it to OCRised historical texts using supervised or unsupervised approaches. This is why, in our tests, we have selected two deep learning-based NER approaches trained on French texts: Spacy 3 NER pipeline and CamemBERT.

>>>>

In our tests, we have selected two deep learning-based NER models trained on French texts: Spacy 3 NER pipeline and CamemBERT. They are adapted to  historical texts as follows.
